---
title: "Quantile Regressions - 1994-2017"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
  word_document: default
---


```{r}
library(dplyr)
library(ggplot2)
library(lubridate)
library(quantreg)
setwd("/Users/whwilson/Desktop/R Files/Arrival Date Project")


```

Load dataset

```{r}
arr <- read.csv("/Users/whwilson/Desktop/R Files/Arrival Date Project/arrivals_1994_2017.csv")


```

Convert to date object, to Julian day and set Biophysical Regions to factors. Exclude 2017 data until NCDC temperature data are available.

```{r}
arr$date <- dmy(arr$Date)
arr$doy <- yday(arr$date)
arr$BioPhyReg <- as.factor(arr$BioPhyReg)
arr <- arr %>%  filter(Year < 2017) %>% filter(doy>31)
str(arr)
```
```{r}
summary(arr)
```
Need to add temperature-departure data when 2017 March, April and May data are available

```{r}
sub <- arr %>% filter(Species == "Alder Flycatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex, 
c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "American Bittern") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "American Kestrel") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")



```

```{r}
sub <- arr %>% filter(Species == "American Redstart") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "American Robin") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "American Woodcock") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Arctic Tern") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Baltimore Oriole") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Bank Swallow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Barn Swallow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Bay-breasted Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Belted Kingfisher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Bicknell's Thrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Black Tern") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Black-and-white Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Black-billed Cuckoo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Black-crowned Night-Heron") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Black-throated Blue Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Black-throated Green Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Blackburnian Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Blackpoll Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Blue-gray Gnatcatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Blue-headed Vireo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Blue-winged Teal") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Blue-winged Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Bobolink") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Broad-winged Hawk") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Brown Thrasher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Brown-headed Cowbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Canada Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Cape May Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Chestnut-sided Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Chimney Swift") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Chipping Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Cliff Swallow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Common Grackle") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Common Loon") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Common Nighthawk") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Common Tern") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Common Yellowthroat") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Eastern Bluebird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Eastern Kingbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Eastern Meadowlark") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Eastern Phoebe") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Eastern Towhee") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Eastern Wood-Pewee") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Field Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Fox Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Glossy Ibis") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Grasshopper Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Gray Catbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Gray-cheeked Thrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Great Blue Heron") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Great Crested Flycatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Green Heron") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Green-winged Teal") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Hermit Thrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "House Wren") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Indigo Bunting") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Killdeer") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Least Flycatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Least Tern") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Lincoln's Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Louisiana Waterthrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Magnolia Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Marsh Wren") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Mourning Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Nashville Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Nelson's Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Northern Flicker") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Northern Harrier") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

Removed Northern Mockingbird. Generates error
```{r}

```

```{r}
sub <- arr %>% filter(Species == "Northern Parula") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Northern Rough-winged Swallow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Northern Waterthrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Olive-sided Flycatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Orchard Oriole") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Osprey") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Ovenbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Palm Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Philadelphia Vireo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Pied-billed Grebe") %>%  
  filter(doy < median(doy) + 21)

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Pine Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Piping Plover") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Prairie Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Purple Martin") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Red-eyed Vireo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Red-winged Blackbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```
Remove late dates
```{r}
sub <- arr %>% filter(Species == "Red-winged Blackbird") %>% 
  filter(doy < median(doy) + 21)

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Ring-necked Duck") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Rose-breasted Grosbeak") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Roseate Tern") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Ruby-crowned Kinglet") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Ruby-throated Hummingbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```
Ruby-throated Hummingbird with late arrivals removed
```{r}
sub <- arr %>% filter(Species == "Ruby-throated Hummingbird") %>% 
  filter(doy < median(doy) + 21)

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Rusty Blackbird") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Salt Marsh Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

Removed Sandhill Crane. Error generated
```{r}

```

```{r}
sub <- arr %>% filter(Species == "Savannah Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Scarlet Tanager") %>% 
  filter(doy < median(doy) + 21)

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Song Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Sora") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Spotted Sandpiper") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Swainson's Thrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Swamp Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Tennessee Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Tree Swallow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Turkey Vulture") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Upland Sandpiper") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Veery") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Vesper Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Virginia Rail") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Warbling Vireo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Whip-poor-will") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "White-throated Sparrow") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Willet") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Willow Flycatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Wilson's Snipe") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Wilson's Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Winter Wren") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Wood Duck") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Wood Thrush") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Yellow Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Yellow-bellied Flycatcher") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Yellow-bellied Sapsucker") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Yellow-billed Cuckoo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Yellow-rumped Warbler") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

```{r}
sub <- arr %>% filter(Species == "Yellow-throated Vireo") 

mod <- rq(sub$doy~sub$Year + sub$TempDepart + sub$NAOIndex,            tau = c(0.1,0.3,0.5))
summary(mod, se = "boot")
```

